\documentclass[12pt]{article}
\usepackage[top=0.75in, bottom=0.75in, left=1in, right=1in]{geometry}
\pagestyle{empty}
\usepackage{tabu}
\usepackage{hyperref}
\usepackage{csvsimple}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\begin{document}

% Course title header
\begin{center}
{\bf NE 24 - Putting the Science in Computational Science \\ M 3:00 - 4:00 pm in 237 Cory
}
\end{center}

\setlength{\unitlength}{1in}
\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}

% Basic Info
\vskip.25in
\noindent\textbf{Instructor:} Rachel Slaybaugh,  4173 Etcheverry Hall,\\ \hspace*{0.95 in}slaybaugh@berkeley.edu,  570-850-3385
\vskip.25in
\noindent\textbf{Office Hours:} 2:30 - 3:30 PM F and by appointment

% Course Description
\vskip.25in
\noindent\textbf{Course Description:}
Is something science if it's not reproducible? How reproducible is the science involving data and computation? Work in these areas is frequently fraught with version, access, and reproducibility problems--resulting in erroneous results and wasting time and energy.
\\

\noindent This course will equip you to begin a career in which you can tackle computational science projects effectively. You will learn
\begin{itemize}
\item how to navigate the command line;
\item how to track and share work over the web; and
\item how to grow a program in a modular, testable, documented, reusable way.
\end{itemize}
These skills will save you time and help you work more effectively in many future classes and in your career. 

% resources
\vskip.25in
\noindent\textbf{Resources:}
\begin{itemize}
  \item Course GitHub page: \href{https://github.com/rachelslaybaugh/NE24}{https://github.com/rachelslaybaugh/NE24}
  \item Software Carpentry's lessons: \href{http://software-carpentry.org/lessons.html}{http://software-carpentry.org/lessons.html}
  \item bCourses site: \href{https://bcourses.berkeley.edu/courses/1457497}{https://bcourses.berkeley.edu/courses/1457497} 
  \item Choose a Python Ebook that fits your needs: \href{http://www.leettips.org/2013/02/top-10-free-python-pdf-ebooks-download.html}{http://www.leettips.org/2013/02/top-10-free-python-pdf-ebooks-download.html}
\end{itemize}

\vskip.25in
\noindent\textbf{the Hacker Within:} 
\begin{itemize}
\item Tuesdays, 4-5:30 pm, 190 Doe Library (BIDS Space)
\item Will teach skills useful for this course
\item Website: \href{http://thehackerwithin.github.io/berkeley/}{http://thehackerwithin.github.io/berkeley/}
\item GitHub: \href{https://github.com/thehackerwithin/berkeley}{https://github.com/thehackerwithin/berkeley}
\end{itemize}

% grading
\clearpage
\noindent\textbf{Grading:} 
\begin{itemize}
\item Homework 50\%
\item Class participation 20\%
\item Final Project 30\% 
\item Late submissions: -20\% for each day it is late
\end{itemize}

% Course Outline
%\vspace*{.15in}
%\noindent \textbf{Course Outline:} 
%\begin{enumerate}
%\item the Unix shell
%\item version control with Git
%\item intro to iPython
%\item documentation
%\item software testing
%\end{enumerate}

\vspace*{.15in}
\noindent \textbf{Useful Campus Information:} 
\begin{itemize}
  \item Mental health resources: \href{http://www.uhs.berkeley.edu/students/counseling/cps.shtml}{http://www.uhs.berkeley.edu/students/counseling/cps.shtml}
  \item Sexual assault support on campus: \href{http://survivorsupport.berkeley.edu/}{http://survivorsupport.berkeley.edu/}
\end{itemize}

\vspace*{.15in}
\noindent\textbf{Academic Honesty}:  Berkeley's honor code is

\begin{quote}
As a member of the UC Berkeley community, I act with honesty, integrity, and respect for others.
\end{quote}

\noindent The University provides some basic guidance about academic integrity: \href{http://sa.berkeley.edu/conduct/integrity}{http://sa.berkeley.\\edu/conduct/integrity}. Lack of knowledge of the academic honesty policy is not a reasonable explanation for a violation. Questions related to course assignments and the academic honesty policy should be directed to me.

\vskip.25in
\noindent My policy is that you may work together on homework, \textbf{but you must specifically site with whom you worked and what you did together}.

\vskip.25in
\noindent\textbf{Extra Help}:  Do not hesitate to come to my office during office hours or by appointment to discuss a homework problem or any aspect of the course. 

\vskip.25in
\noindent\textbf{Attendance}: Students are expected to attend classes regularly. A student who incurs an excessive number of absences may be withdrawn from this class at my discretion.

\vskip.25in
\noindent\textbf{Other Policies}: This course abides by the university policies for
\begin{itemize}
  \item accommodation of religious creed \href{http://registrar.berkeley.edu/DisplayMedia.aspx?ID=Religious\%20Creed\%20Policy.pdf}{http://registrar.berkeley.edu/DisplayMedia.aspx?ID\\=Religious\%20Creed\%20Policy.pdf}, and
  \item conflicts between extracurricular activities and academic requirements \href{http://academic-senate.berkeley.edu/sites/default/files/committees/cep/guidelines\_acadschedconflicts\_final\_2014.pdf}{http://academic-senate.berkeley.edu/sites/default/files/committees/cep/guidelines\_acadschedconflicts\\\_final\_2014.pdf}.
  \item In case of illness please do not come to class if you have a fever or something highly contagious. Please do if there is any chance you will pay attention and not get other sick: \href{http://academic-senate.berkeley.edu/committees/coci/toolbox\#16}{http://academic-senate.berkeley.edu/committees/coci/toolbox\#16}.
\end{itemize}


%-----------------------------------------------------------------------------
\clearpage
\noindent\textbf{Schedule}: \textit{Note that this is subject to change}\\
Please check the github page for up-to-date data.
\begin{table}[htbp]
\begin{tabular}{|r|r|l|}
\hline
\multicolumn{1}{|c|}{Lecture} & \multicolumn{1}{c|}{Date} & \multicolumn{1}{c|}{Topic} \\ \hline
1  & 23-Jan & \href{http://rachelslaybaugh.github.io/NE24/intro/#/}{introduction} \\ \hline
2  & 30-Jan & \href{http://bids.github.io/2016-01-14-berkeley/shell/}{shell} \\ \hline
3  & 6-Feb  & \href{http://bids.github.io/2016-01-14-berkeley/git/}{Git local} \\ \hline
4  & 13-Feb & \href{http://bids.github.io/2016-01-14-berkeley/git/}{Git remote} \\ \hline
%2  & 30-Jan & \href{https://github.com/rachelslaybaugh/shell-novice}{shell} \\ \hline
%3  & 6-Feb  & \href{https://github.com/rachelslaybaugh/git-novice}{Git local} \\ \hline
%4  & 13-Feb & \href{https://github.com/rachelslaybaugh/git-novice}{Git remote} \\ \hline
-  & 20-Feb & \textit{President's Day} \\ \hline

5  & 27-Feb & \href{https://github.com/rachelslaybaugh/ucb-ipython-intro}{iPython} \\ \hline
6  & 6-Mar & \href{https://github.com/rachelslaybaugh/NE24/blob/master/project.md}{projects} \\ \hline%+ \href{http://thehackerwithin.github.io/berkeley/posts/numpy-vectorization/}{guest lecture} ;
7  & 12-Mar &  \href{http://rachelslaybaugh.github.io/python-testing/}{unit testing} \\ \hline
-  & 20-Mar & \href{http://rachelslaybaugh.github.io/python-testing/}{in-code testing}\\ \hline
%7  & 12-Mar &  \href{http://rachelslaybaugh.github.io/NE24/testing/Testing.pdf}{unit testing} \\ \hline %\href{https://github.com/thehackerwithin/berkeley/tree/master/python_logger}{materials}\\ \hline
%-  & 20-Mar & \href{http://rachelslaybaugh.github.io/NE24/testing/Testing.pdf}{in-code testing} ; \href{http://rachelslaybaugh.github.io/NE24/testing/test-except.pdf}{and exceptions} \\ \hline
8  & 28-Mar & \textit{spring break} \\ \hline
9  & 3-Apr  & \href{https://github.com/rachelslaybaugh/NE24/tree/master/documentation}{documentation} \\ \hline
10 & 10-Apr & \href{https://github.com/garretchristensen/LaTeXIntro}{\LaTeX} \\ \hline
%10 & 10-Apr & \href{https://github.com/rachelslaybaugh/NE24/tree/master/LaTeX}{\LaTeX} \\ \hline
11 & 17-Apr & careers \\ \hline
12 & 24-Apr & in-class presentations \\ \hline
\end{tabular}
\end{table}




\end{document}
